Discovering Focused Microgenre Communities: Toy example

### 2023-08-04 qmd/04_microgenre-analysis.qmd
New dends

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(ggplot2)
    library(haven)
    library(here)
    library(sjPlot)
    library(tidyverse)
    library(webshot)
    load(file= here("dat", "lclust-res.RData"))
```

@@

```{r Microgenre Regression Plots (Age)}
    age.preds <- pred.probs(x = "age.n", res.metal$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    ym = -0.02,
                    yl = .2, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-metal.png"), 
              fig = p,
              height = 25, width = 20)

    age.preds <- pred.probs(x = "age.n", res.salsa$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    ym = -0.02,
                    yl = .16, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-salsa.png"), 
              fig = p,
              height = 25, width = 20)
```
`

>>>>

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(ggplot2)
    library(here)
    library(sjPlot)
    library(tidyverse)
    library(webshot)
    load(file= here("dat", "lclust-res.RData"))
```

@@

```{r Microgenre Regression Plots (Age)}
    age.preds <- pred.probs(x = "age.n", res.metal$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Middle Aged", "Old"),
                    ym = -0.02,
                    yl = .2, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-metal.png"), 
              fig = p,
              height = 25, width = 20)

    age.preds <- pred.probs(x = "age.n", res.salsa$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Middle Aged", "Old"),
                    ym = -0.02,
                    yl = .16, 
                    xm = 2, 
                    xl = 12)
    save_plot(filename = here("Plots", "Micro", "micro-by-age-salsa.png"), 
              fig = p,
              height = 25, width = 20)
```
`
